\documentclass[showpacs,preprintnumbers,prb]{revtex4}
\usepackage{graphicx,amssymb,amsmath}
\usepackage[usenames]{xcolor}
\newcommand{\etalter}{{\it et al.}}
\newcommand{\eg}{{\it e.\ g.}}
\newcommand{\ie}{{\it i.\ e.}}

\begin{document}

\title{Title goes here}
\author{G. Alvarez}
\affiliation{Computer Science \& Mathematics 
Division and Center for Nanophase Materials Sciences, Oak Ridge National Laboratory, \mbox{Oak Ridge, TN 37831}}

\author{A. Nocera}
\affiliation{Computer Science \& Mathematics 
Division and Center for Nanophase Materials Sciences, Oak Ridge National Laboratory, \mbox{Oak Ridge, TN 37831}}

\begin{abstract}
Here goes the abstract....
\end{abstract}

\maketitle
\section{Entaglement Entropy}
\subsection{Criticality}
We are going to work with a class $\mathcal{C}$ of strongly correlated Hamiltonians that
are short-ranged in some $d$ dimensional geometry.
A system is critical if it is gapless \emph{and} $d-d_\Gamma=1$, where $d$ is the
dimension of the geometry, and $d_\Gamma$ the dimension of the Fermi surface.
See citation at the end.

\subsection{Properties of ``Area Laws'' Hamiltonians}

The ground state of a strongly correlated 
Hamiltonian $H\in\mathcal{C}$ in $d=1$ noncritical has a entaglement entropy 
$S_\text{exact} \propto C$, where $C$ is a constant independent of system length $L$. 
The ground state of a strongly correlated  Hamiltonian $H\in\mathcal{C}$ 
 in $d=1$ critical has a entaglement entropy 
$S_\text{exact} \propto \ln(L)$.
The ground state of a strongly correlated  Hamiltonian $H\in\mathcal{C}$
in $d>1$ noncritical has a entaglement entropy 
$S_\text{exact} \propto L^{d-1}$, and for critical it is $L^{d-1}\ln{L}$.

\subsection{DMRG and MPS}
The entaglement entropy of a MPS of length $L^d$ and bond dimension $m$
is $S_\text{MPS}(L^d,m) \propto \ln(m)$. 
To match the entaglement entropy growth, the $m$ required to simulate a problem 
with MPS or DMRG is as follows: $m\propto C$ for $d=1$ noncritical, $m\propto L$ for
$d=1$ critical, $m\propto \exp(L^{d-1})$ for $d>1$ noncritical and
$m\propto L^{L^{d-1}}$ for $d>1$ critical.

\subsection{PEPS}
The entaglement entropy of PEPS with length $L$ and bond dimension $m$
is $S_\text{PEPS}(L,d,m) \propto L^{d-1}\ln(m)$.
To match the entaglement entropy growth, the $m$ required to simulate a problem 
with PEPS is as shown in the table. Note that even though the PEPS has
large entropy and thus should produce good scaling for $m$, the main problem of
PEPS is that contraction has exponential cost.

\subsection{MERA}
The entaglement entropy of scale invariant 
MERA with length $L$, dimension $d=1$, and bond dimension $m$
is $S_\text{MERA}(L,d=1,m) \propto \ln(L)\ln(m)$.
The entaglement entropy of MERA with length $L$, dimension $d>1$, and bond dimension $m$
is $S_\text{MERA}(L,d,m) \propto L^{d-1}\ln(m)$.
To match the entaglement entropy growth, the $m$ required to simulate a problem 
with MERA is as shown in the table.
\end{document}
%@article{PhysRevB.89.235113,
%  title = {Scaling of entanglement entropy in the (branching) multiscale entanglement renormalization ansatz},
%  author = {Evenbly, G. and Vidal, G.},
%  journal = {Phys. Rev. B},
%  volume = {89},
%  issue = {23},
%  pages = {235113},
%  numpages = {15},
%  year = {2014},
%  month = {Jun},
%  publisher = {American Physical Society},
%  doi = {10.1103/PhysRevB.89.235113},
%  url = {http://link.aps.org/doi/10.1103/PhysRevB.89.235113}
%}
